Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-08-07 paperIEEE.tex
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@143 db7c848b-7755-4df2-b763-8796797afa52

Tile (\fig{fig:tiles}) and chunk decompositions are a variant of sort-first and
sort-last rendering, respectively. They decompose the scene into a predefined
set of fixed-size image tiles or database ranges. These tasks, or work packages,
are queued and processed by all source channels by polling a server-central
queue. Prefetching ensures that the task communication overlaps with rendering.
As shown in~\cite{SPEP:16} and the results, these modes can provide better
performance due to being implicitly, i.e., inherently load-balanced, as long as
there is an insignificant overhead for the render task setup. This mode is
transparent to \textsf{Equalizer} applications.

@@

For sort-first and sort-last rendering we present static and load-balanced task
decomposition. For readability, we only present the results of the equalizer
(load or tree) providing the better performance for each application.
Unsurprisingly, static decompositions perform worse over load-balanced
compounds. Sort-first polygon rendering exhibits oscillations in performance as
nodes are added to the task, due to unfavorable assignment of a tile with a high
work load on odd node counts. Static sort-last volume rendering has a similar
oscillation behaviour, as ranges of scene geometry tend to also get unfavorably
assigned under such conditions.

@@

This figure gives an impression of how individual modes perform on heterogeneous
systems. In this case the tree equalizer performs best (\fig{fEqualizers}
(left)), as it allows us to a priori define how much {\em usage} it should make
of individual nodes, i.e., bias the allocation of rendering time in accordance
with the (simulated) compute resources. \fig{fEqualizers} (right), on the other
hand, illustrates how the tested decomposition modes perform on a system where
compute resources fluctuate randomly every frame, as can arguably be the case
for shared rendering nodes in virtualized enviroments. For this scenario tile
equalizer seems best suited, as it performs load balancing implicitly and does
not assume coherence of available resources between frames. The simpler tree
equalizer also outperforms the load equalizer in this experiment.

>>>>

Tile (\fig{fig:tiles}) and chunk decompositions are a variant of sort-first and
sort-last rendering, respectively. They are implemented via the \textsf{tile\_equalizer} and \textsf{chunk\_equalizer} compounds, which decompose the scene into a predefined
set of fixed-size image tiles or database ranges, respectively.
The resulting tasks, or work packages,
are queued and processed by all source channels by polling a server-central
queue. Prefetching ensures that the task communication overlaps with rendering.
As shown in~\cite{SPEP:16} and the results, these modes can provide better
performance due to being implicitly, i.e., inherently load-balanced, as long as
there is an insignificant overhead for the render task setup. This mode is
transparent to \textsf{Equalizer} applications.

@@

For sort-first and sort-last rendering we present static and load-balanced task
decomposition. For readability, we only present the results of the equalizer
(load or tree) providing the better performance for each application.
Unsurprisingly, static decompositions perform worse over load-balanced
compounds. Sort-first polygon rendering exhibits oscillations in performance as
nodes are added to the task, due to unfavorable assignment of a tile with a high
work load on odd node counts. Static sort-last volume rendering has a similar
oscillation behaviour, as ranges of scene geometry tend to also get unfavorably
assigned under such conditions. It seems plausible that this is also due to overheads associated with these two rendering scenarios. That is, volume rendering typically benefits less form sort-last decompositions, because of higher costs for compositing. Similarly, polygonal rendering often benefits less from sort-first decomposition, as compositing costs are typically much lower, while culling of geometry can create an additional overhead.

@@

This figure gives an impression of how individual modes perform on heterogeneous
systems. In this case the tree equalizer performs best (\fig{fEqualizers}
(left)), as it allows us to a priori define how much {\em usage} it should make
of individual nodes, i.e., bias the allocation of rendering time in accordance
with the (simulated) compute resources. \fig{fEqualizers} (right), on the other
hand, illustrates how the tested decomposition modes perform on a system where
compute resources fluctuate randomly every frame, as can arguably be the case
for shared rendering nodes in virtualized enviroments. For this scenario \textsf{tile\_equalizer} seems best suited, as it performs load balancing implicitly and does
not assume coherence of available resources between frames. The simpler tree
equalizer also outperforms the \textsf{load\_equalizer} in this experiment.
